article title

### 2022-07-25 pilon_gilles_glossary.tex
Add specification
Add plural to specification
Add variance

@@

>>>>

\newglossaryentry{specification}
    name={specification},
    description={In the context of measurement system analysis, process capability, and process control, a specification is a lower limit, a target, and an upper limit},
    plural={specifications}

@@

\newglossaryentry{variance}
    name={variance},
    description={It is a measure of dispersion, how far a set of numbers is spread out from their average. It is the expectation of the squared devitaion of a random variable from its population average or sample saverage.}
    plural={variances}
